
\subsection{What is Citadel} 

A Self-Sovereign Identity (SSI) protocol serves the purpose of allowing users of a given service to manage their identities in a fully transparent manner. In other words, every user can know which information about them is shared with other parties, and accept or deny any request for personal information.

\verb!Citadel! is a SSI protocol built on top of Dusk. Users of a service can get a \textit{license}, which represents their \textit{right} to use such a service. In particular, \verb!Citadel! allows for the following properties:

\begin{itemize}
	\item \textbf{Proof of Ownership:} users can prove ownership of a license that allows them to use a given service.
	\item \textbf{Proof of Validity:} users can prove that a license has not been revoked and hence, it is a valid license.
 	\item \textbf{Unlinkability:} activities from the same user in the network cannot be linked to each other by other parties.
 	\item \textbf{Decentralized Session Opening:} when users use a license to open a session to use a service, everyone in the network learns that this happened, so it cannot be used again.
	\item \textbf{Attribute Blinding:} users can decide what information they want to share, hiding any other sensitive information and providing only the desired one.
\end{itemize}

\subsection{Document Organization} 

In Section \ref{sec:definitions}, we define all the object types and entities involved in the protocol. In Section \ref{sec:protocol}, we roll out the protocol with full details.